---
title: "Meat production and consumption in world"
subtitle: "TBIR"
author: "Cui Di, GuanRu Chen, Yunzhi Chen"
institute: "Master of Business Analytics"
output:
  xaringan::moon_reader:
    
    lib_dir: libs
    css: ["xaringan-themer.css"]
    yolo: FALSE
editor_options: 
  chunk_output_type: console
---



class: left, top

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r libraries, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(datasets)
library(readr)
library(kableExtra)
library(bookdown)
library(gridExtra)
library(viridis)
library(plotly)
library(emo)
library(xaringanthemer)
style_mono_accent(base_color = "#43418A")

```

# Outline
### `r emo::ji("target")`Global meat production -- Di Cui
### `r emo::ji("target")`Meat production by livestock type -- GuanRu Chen
### `r emo::ji("target")`Per capita meat consumption -- Yunzhi Chen

---
class: left, top
# `r emo::ji("book")`Introduction

Feeding the world in a sustainable way is one of our most pressing challenges in the coming decades. Meat plays a pivotal role in this.

Meat is an important source of nutrition for many people around the world. Therefore, global demand for meat is keep growing: over the past 50 years, meat production has more than tripled. The world now produces more than 340 million tonnes each year.

The data set was obtained from the "Our World in Data" data base and contains the following variables regarding to meat production of the world:
 
* Country
* Year
* Amount of production: Measure in tons.
* Livestock types: including beef and buffalo, pigmeat, poultry, sheep and goat,  and other meat types such as horse or camel et cetera.
* Meat type consumption (kg/capita/year).


---
class: center, middle
# `r emo::ji("meat")`Global meat production


---
class: left, top
# Research Questions


- How did the global meat production develop by continents?

- How did the meat production develop in countries which contributed greatly?



---
## How did the global meat production develop by continents?

```{r Q1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap="Global meat production from 1961 to 2018", fig.width=10, fig.height=5, fig.align='center'}

global_production <-read.csv(here::here("Data/global-meat-production.csv"))
production <- read.csv(here::here("Data/meat-production-tonnes.csv"))

global_production <- global_production %>%
  rename("meat_production" = "Livestock.Primary...Meat..Total...1765...Production...5510...tonnes") %>%
  mutate(meat_production = round(meat_production/1000000, digits = 2)) %>%
  filter(Entity %in% c("Oceania", "Africa", "Central America", "South America", "Northern America", "Europe", "Asia")) 

df <- global_production %>%
  group_by(Entity) %>%
  mutate(meat_sum = sum(meat_production)) %>%
  ungroup() %>%
  arrange(meat_sum) 

df <- df %>%
  mutate(Entity = factor(Entity, unique(Entity))) %>%
  group_by(Year) %>%
  mutate(total = sum(meat_production))

ggplot(df, aes(x = Year, y = meat_production, color = Entity))+
  geom_line()+
  scale_fill_brewer(palette = "Set3")+
  scale_x_continuous(breaks = c(1961,1970,1980, 1990, 2000, 2010,2018))+
  scale_y_continuous(breaks = c(0, 10, 50, 100, 150))+
  ylab("livestock meat production (million tonnes)")+
  theme_bw()

```

- Asia has been the largest meat producer since 1992.

---
class: left, top


```{r table, echo = FALSE, message = FALSE, warning = FALSE}
increase <- df %>%
  filter(Year == 2018 | Year == 1961) %>%
  select(Entity, Year, meat_production) %>%
  pivot_wider(names_from = Year, values_from = meat_production) %>%
  rename("Year2018" = "2018", "Year1961" = "1961" ) %>%
  mutate(P1961 = round(Year1961*100/sum(Year1961), digits = 2)) %>%
  mutate(P2018 = round(Year2018*100/sum(Year2018), digits = 2)) %>%
  mutate(times = round((Year2018-Year1961)/Year1961, digits = 2)) 
increase %>%
  arrange(-P2018)%>%
  knitr::kable(caption = "Comparison between 1961 and 2018") %>%
  kable_styling()

```

- Meat production in Asia has increased around **15** times, accounting for around **43%** of total global meat production.

---

## How did the meat production develop in countries which contributed greatly?

```{r country, echo = FALSE, message = FALSE, warning = FALSE, fig.cap="Top six countries' meat production from 1961 to 2018", fig.width=10, fig.height=5, fig.align='center'}
production <- production %>%
   rename("meat_production" = "Livestock.Primary...Meat..Total...1765...Production...5510...tonnes") %>%
  mutate(meat_production = round(meat_production/1000000, digits = 2)) 

df2 <- production %>%
  group_by(Entity) %>%
  mutate(meat_sum = sum(meat_production)) %>%
  ungroup() %>%
  arrange(-meat_sum) 

df2 <- df2 %>%
  filter(Code != "" &
        Code %in% c("CHN", "USA", "BRA", "DEU", "FRA", "ARG"))

ggplot(df2, aes(x = Year, y = meat_production, color = Entity))+
  geom_line()+
  scale_fill_brewer(palette = "Set3")+
  scale_x_continuous(breaks = c(1961,1970,1980, 1990, 2000, 2010,2018))+
  ylab("Top 6 countries of livestock meat production (million tonnes)")+
  theme_bw()

ggplotly()

```

- China has become the largest meat production country in the world since 1990.

---

```{r country-table, echo = FALSE, message = FALSE, warning = FALSE}
increase2 <- production %>%
  group_by(Entity) %>%
  filter(Code != "" &
        Code %in% c("CHN", "USA", "BRA", "DEU", "FRA", "ARG" ,"OWID_WRL"))%>%
  filter(Year == 2018 | Year == 1961) %>%
  select(Entity, Year, meat_production) %>%
  pivot_wider(names_from = Year, values_from = meat_production) %>%
  rename("Year2018" = "2018", "Year1961" = "1961" ) %>%
  mutate(P1961 = round(Year1961*100/71.36, digits = 2)) %>%
  mutate(P2018 = round(Year2018*100/342.42, digits = 2)) %>%
  mutate(times = round((Year2018-Year1961)/Year1961, digits = 2)) 
  

increase2 %>%
  arrange(-P2018)%>%
  knitr::kable(caption = "Comparison between 1961 and 2018") %>%
 kable_styling()


```

-The world's meat production has around quadrupled.

-China has increased about 34 times.

**Although these Entities have increased, their proportion has changed a lot. In 2018, Asia and China cover a large proportion of the global meat production.**

---
class: center, middle
# `r emo::ji("meat")`Meat production 
# by livestock type


---
class: left, top
# `r emo::ji("notebook")`Research Questions

 
- What's the production distribution of different livestock types across the world?

- Which countries are main production country for different types of meat, such as: Beef and buffalo, pig and poultry?



---
class: left, top

## What's the production distribution of different livestock types across the world?
```{r load-data, echo = FALSE , message = FALSE, warning = FALSE}
GD <- read_csv(file = "Data/global-meat-production.csv")
MT <- read_csv(file = "Data/global-meat-production-by-livestock-type.csv")
```

```{r fig1, echo = FALSE , message = FALSE, warning = FALSE, fig.cap = "Global meat production by livestock type, 1961 to 2018", fig.height = 3, fig.width = 10, fig.align='center'}
production <- GD %>%
  select(-Code) %>% 
  filter(Entity %in% c("Asia",
                       "Europe",
                       "Northern America",
                       "South America",
                       "Central America",
                       "Africa",
                       "Oceania")) %>%
    rename("Production"= "Livestock Primary - Meat, Total - 1765 - Production - 5510 - tonnes") %>%
    group_by(Entity, Year) %>% 
    mutate(Sum = round(Production/1000000, digits = 2))

plt_pd<- ggplot(production, aes(x= Year,
                                y= Sum, 
                                fill= Entity)) + 
    geom_area(alpha=0.6 , size=.5, colour="white")+
    scale_fill_viridis(discrete = T) +
    theme_minimal()+
    ggtitle("Global meat production, 1961 to 2018")+
    ylab("Production (million tonnes)")
plt_pd
```

In first figure, we see that the **dominant livestock types are poultry**, cattle (which includes beef and buffalo meat), pig, and sheep & goat to a lesser extent at global level.


---
class: left, top
```{r fig2, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Meat production by livestock type, 1961 to 2018", fig.height = 6, fig.width = 12, fig.align='center'}
pt_world <- MT %>%
  select(-Code) %>% 
  rename("Sheep & Goat"= "Livestock Primary - Sheep and Goat Meat - 1807 - Production - 5510 - tonnes",
         "Beef & Buffalo"= "Livestock Primary - Beef and Buffalo Meat - 1806 - Production - 5510 - tonnes",
         "Pig"= "Livestock Primary - Meat, pig - 1035 - Production - 5510 - tonnes",
         "Wild Game"= "Livestock Primary - Meat, game - 1163 - Production - 5510 - tonnes",
         "Duck"= "Livestock Primary - Meat, duck - 1069 - Production - 5510 - tonnes",
         "Poltry"= "Livestock Primary - Meat, Poultry - 1808 - Production - 5510 - tonnes",
         "Horse"= "Livestock Primary - Meat, horse - 1097 - Production - 5510 - tonnes",
         "Camel"= "Livestock Primary - Meat, camel - 1127 - Production - 5510 - tonnes",
         "Goose & Guinea fowl"= "Livestock Primary - Meat, goose and guinea fowl - 1073 - Production - 5510 - tonnes") %>%
  filter(Entity== "World") %>% 
  group_by(Entity, Year) 

pt_world_long <- pt_world %>% 
  pivot_longer(cols= "Sheep & Goat":"Goose & Guinea fowl",
               names_to= "Type",
               values_to = "Amount") %>% 
  mutate(Sum = round(Amount/1000000, digits = 2))


plt_type<- ggplot(pt_world_long, aes(x= Year,
                                     y= Sum,
                                     group= Type,
                                     fill= Type))+
    geom_area() +
    scale_fill_viridis(discrete = TRUE)+
    theme_minimal() +
    facet_wrap(~ Type, scale="free_y")+
    ylab("Production by livestiock type (million tonnes)")

plt_type
```

From second figure, we can see the production of all major meat types have been increasing. But **the share of global meat types have changed significantly**. 
  - In 1960s poultry meat accounted for small portion; by 2010s its share has tripled. 
  - Beef and buffalo meat as a share of total meat production has nearly halved. 
  - Pig meat’s share has remained more constant.

---
class: left, top
## Which countries are main production country for different types of meat, such as: Beef and buffalo, pig and poultry?

---
class: middle, top
```{r tidydata, echo = FALSE , message = FALSE, warning = FALSE}
pd_type <- MT %>%
  select(-Code) %>% 
  rename("Sheep & Goat"= "Livestock Primary - Sheep and Goat Meat - 1807 - Production - 5510 - tonnes",
         "Beef & Buffalo"= "Livestock Primary - Beef and Buffalo Meat - 1806 - Production - 5510 - tonnes",
         "Pig"= "Livestock Primary - Meat, pig - 1035 - Production - 5510 - tonnes",
         "Wild Game"= "Livestock Primary - Meat, game - 1163 - Production - 5510 - tonnes",
         "Duck"= "Livestock Primary - Meat, duck - 1069 - Production - 5510 - tonnes",
         "Poultry"= "Livestock Primary - Meat, Poultry - 1808 - Production - 5510 - tonnes",
         "Horse"= "Livestock Primary - Meat, horse - 1097 - Production - 5510 - tonnes",
         "Camel"= "Livestock Primary - Meat, camel - 1127 - Production - 5510 - tonnes",
         "Goose & Guinea fowl"= "Livestock Primary - Meat, goose and guinea fowl - 1073 - Production - 5510 - tonnes") %>%
    group_by(Entity, Year) %>%
    pivot_longer(cols= "Sheep & Goat":"Goose & Guinea fowl",
               names_to= "Type",
               values_to = "Amount")
```

```{r cattle, echo = FALSE , message = FALSE, warning = FALSE}
pd_cattle <- pd_type %>% 
    filter(Type == "Beef & Buffalo") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>%
    mutate(Production = round(Total/1000000, digits = 2)) %>% 
    select(-Total) %>%
    arrange(-Production)

kable(head(pd_cattle, 20), caption = "Beef and buffalo (cattle) meat production (million tonnes), 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center") %>% 
  scroll_box(width = "800px", height = "600px")
```


---
class: left, top
```{r cattle-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Cattle production, 1961 to 2018", fig.height = 9, fig.width = 15, fig.align='center'}
top_cattle<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Brazil")) %>% 
  filter(Type== "Beef & Buffalo") %>% 
  mutate(Production = round(Amount/1000000, digits = 2)) %>%
  group_by(Entity)

ggplot(top_cattle, aes(x= Year, y= Production, color= Entity))+
    geom_line()+
    scale_fill_viridis(discrete = TRUE) +
    ylab("Production (million tonnes)")+
    theme_minimal()
```

In first table, we see the global production of cattle (beef and buffalo) meat. From country's perspective, **The United States is the world’s largest beef and buffalo meat producer**. Other major producers are Brazil and China.

---
class: middle, top
```{r poultry, echo = FALSE , message = FALSE, warning = FALSE}
pd_poultry <- pd_type %>% 
    filter(Type == "Poultry") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>%
    mutate(Production = round(Total/1000000, digits = 2)) %>%
    select(-Total) %>%
    arrange(-Production)

kable(head(pd_poultry, 20), caption = "Poultry meat production (million tonnes), 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center") %>% 
  scroll_box(width = "800px", height = "600px")
```



---
class: left, top
```{r poltry-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "poultry production, 1961 to 2018", fig.height = 9, fig.width = 15, fig.align='center'}
top_poultry<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Brazil",
                       "Europe")) %>% 
  filter(Type== "Poultry") %>% 
  mutate(Production = round(Amount/1000000, digits = 2)) %>%
  group_by(Entity)

ggplot(top_poultry, aes(x= Year, y= Production, color= Entity))+
    geom_line()+
    scale_fill_viridis(discrete = TRUE) +
    ylab("Production (million tonnes)")+
    theme_minimal() 
```

In second table, we can see the production of poultry, like cattle production, **the United States is still the world’s largest producer.** China and Brazil are also large poultry producers. Collectively, Europe is also a major poultry producer, just below the United States.

---
class: middle, top
```{r pig, echo = FALSE , message = FALSE, warning = FALSE}
pd_pigmeat <- pd_type %>% 
    filter(Type == "Pig") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>%
    mutate(Production = round(Total/1000000, digits = 2)) %>%
    select(-Total) %>% 
    arrange(-Production)

kable(head(pd_pigmeat, 20), caption = "Pig meat production (million tonnes), 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center")%>% 
  scroll_box(width = "800px", height = "600px")
```

---
class: left, top
```{r pig-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "pig production, 1961 to 2018", fig.height = 9, fig.width = 15, fig.align='center'}
top_pigmeat<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Germany")) %>% 
  filter(Type== "Pig") %>% 
  mutate(Production = round(Amount/1000000, digits = 2)) %>%
  group_by(Entity)

ggplot(top_pigmeat, aes(x= Year, y= Production, color= Entity))+
    geom_line()+
    scale_fill_viridis(discrete = TRUE) +
    ylab("Production (million tonnes)")+
    theme_minimal()
```

But for pigmeat production , **China dominates global output, producing just short of half of total pigmeat.** The other major producers include the United States, Germany.

---
class: center, middle
# `r emo::ji("meat")`Per capita meat consumption


---
class: left, top
# `r emo::ji("notebook")`Research Questions


- Which countries eat the most meat in the last 20 years?

- What types of meat do people eat?



```{r read-data, echo = FALSE, message = FALSE}
# Read data
meat_consumption_total <- read.csv(here::here("Data/meat-supply-per-person.csv"))
meat_consumption_type <- read.csv(here::here("Data/per-capita-meat-consumption-by-type-kilograms-per-year.csv"))
meat_consumption <- meat_consumption_type %>% left_join(meat_consumption_total) %>%
  rename(Country = Entity,
         Mutton_Goat = Mutton...Goat.meat.food.supply.quantity..kg.capita.yr...FAO..2020.,
         Other_meats = Meat..Other..Food.supply.quantity..kg.capita.yr...FAO..2020.,
         Poultry = Poultry.meat.food.supply.quantity..kg.capita.yr...FAO..2020.,
         Pork = Pigmeat.food.supply.quantity..kg.capita.yr...FAO..2020.,
         Beef_Bufallo = Bovine.meat.food.supply.quantity..kg.capita.yr...FAO..2020.,
         Total_consumption_kg_capita_yr = Meat.food.supply.quantity..kg.capita.yr...FAO..2020.) %>%
  na_if("") %>%
  filter(complete.cases(Code)) %>%
  filter(Country != "Hong Kong" & Country != "Taiwan")

```



---
class: left, top
## Which countries eat the most meat in the last 20 years?

```{r highest-meanconsumption, echo = FALSE}

highest_meanconsumption <- meat_consumption %>% 
                 filter(Year >= 1997) %>%
                 group_by(Country) %>%
                 summarise(Mean_consumption_kg_capita_yr = mean(Total_consumption_kg_capita_yr)) %>%
                 arrange(desc(Mean_consumption_kg_capita_yr)) %>%
                 select(Country, Mean_consumption_kg_capita_yr)

table_data2 <- head(highest_meanconsumption, 6)

knitr::kable(table_data2,
             caption = "Top 6 countries with the largest mean of meat consumption over years", digits = 2) 
```

- The top six countries are the United States, Australia, New Zealand, Spain, French Polynesia and Bahamas.

???
The top six countries with the highest average meat consumption mean in the world over the 20-year period from 1997 to 2017 are the United States, Australia, New Zealand, Spain, French Polynesia and Bahamas. The highest per capita meat consumption mean of the United States reached about 121.2 kg/capita/year. Countries with high income also consume more meat. Developed countries account for a large share of the six countries with the highest average meat consumption over years.

---
class: left, top
## Which countries eat the most meat in the last 20 years?


```{r highest-consumption-trend, echo = FALSE,  fig.height=5, fig.width=9, fig.cap = "Consumption trend of top 6 countries"}
highest_consumption_trend <- meat_consumption %>% 
             filter(Year >= 1997) %>%
             filter(Country %in% c("United States", 
                                   "Australia", 
                                   "New Zealand", 
                                   "Spain", 
                                   "French Polynesia", 
                                   "Bahamas",
                                   "World")) 

ggplot(highest_consumption_trend, 
      aes(x = Year, 
          y = Total_consumption_kg_capita_yr, 
          color = Country)) + 
 geom_line()  

```

- Considerable fluctuation trends, overall downward trends except Australia and the United States.
- Total value is much higher than the world consumption.

???
The meat consumption per person in these countries over the last 20 years have fluctuated considerably, with the exception of Australia and the United States, where consumption has increased, while all other countries have shown a decreasing trend, but the total value is still much higher than the world per capita meat consumption.


---
class: left, top
## What types of meat do people eat?

```{r Meat-type, echo = FALSE, include = FALSE, fig.height=5, fig.width=9, fig.cap = "Meat type changes over time"}
Meat_type <- meat_consumption %>% filter(Country == "World") %>%
  pivot_longer(col = Mutton_Goat:Beef_Bufallo,
               names_to = "Type",
               values_to = "Per_capita_meat_consumption_by_type")

ggplot(Meat_type, 
      aes(x = Year, 
          y = Per_capita_meat_consumption_by_type,
          fill = Type)) + 
 scale_x_continuous(
    breaks = seq(min(Meat_type$Year),
                 max(Meat_type$Year), by=4))+
 geom_col() 

```

```{r show-label, echo = FALSE, fig.height = 5, fig.width = 9}

ggplotly()

```

- Pork has the highest per capita consumption of meat commodities.
- In 2013, pork: 16 kg; poultry: 15 kg; beef & buffalo: 9 kg; lamb & goat: 2 kg; and only a small percentage of other meats.


???
As a global average, pork has the highest per capita consumption of meat commodities; in 2013, per capita pork consumption was about 16 kg; followed by 15 kg of poultry; 9 kg of beef/buffalo meat; 2 kg of lamb and goat; and only a small percentage of other meats.

---
class: left, top
# `r emo::ji("scientist")`Conclusion

- In 2018, production was around 340 million tonnes. And Asia and China have contributed greatly to global meat production.
- The amount of meat produced for a given animal varies significantly across the world based on production systems.
- Richer countries tend to consume more meat per person. Developed countries account for a large share of the six countries with the highest average meat consumption in the last 20 years. 
- The average person in the world consumed around 43 kilograms of meat in 2014. This ranges from over 100kg in the US and Australia to only 5kg in India.
- Although there is a lot of fluctuation, the amount of meat consumed per capita is much larger than the world average.
- At the world level, per capita consumption of pork is the highest among meat commodities over years. 




---
class: center, middle
# Question & Answer


