---
title: "Xaringan Template"
subtitle: "An example"
author: "- Cui, Di", "GuanRu, Chen", "Yunzhi, Chen"
institute: "Master of Business Analytics"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: css/style.css
    yolo: FALSE
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r libraries, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(datasets)
library(readr)
library(kableExtra)
library(bookdown)
library(gridExtra)
library(viridis)
```

---
class: center, middle
# Meat production by livestock type
Presenter:GaunRu Chen.

---
class: left, top
# Research Questions

.content-box-neutral[ 
- What's the production distribution of different livestock types across the world?
- Which countries are main production country for different types of meat, such as: Beef and buffalo, pig and poultry?
]


---
class: middle, center

```{r load-data, echo = FALSE , message = FALSE, warning = FALSE}
GD <- read_csv(file = "Data/global-meat-production.csv")
MT <- read_csv(file = "Data/global-meat-production-by-livestock-type.csv")
```

```{r fig1, echo = FALSE , message = FALSE, warning = FALSE, fig.cap = "Global meat production by livestock type, 1961 to 2018"}
pt_world <- MT %>%
  select(-Code) %>% 
  rename("Sheep & Goat"= "Livestock Primary - Sheep and Goat Meat - 1807 - Production - 5510 - tonnes",
         "Beef & Buffalo"= "Livestock Primary - Beef and Buffalo Meat - 1806 - Production - 5510 - tonnes",
         "Pig"= "Livestock Primary - Meat, pig - 1035 - Production - 5510 - tonnes",
         "Wild Game"= "Livestock Primary - Meat, game - 1163 - Production - 5510 - tonnes",
         "Duck"= "Livestock Primary - Meat, duck - 1069 - Production - 5510 - tonnes",
         "Poltry"= "Livestock Primary - Meat, Poultry - 1808 - Production - 5510 - tonnes",
         "Horse"= "Livestock Primary - Meat, horse - 1097 - Production - 5510 - tonnes",
         "Camel"= "Livestock Primary - Meat, camel - 1127 - Production - 5510 - tonnes",
         "Goose & Guinea fowl"= "Livestock Primary - Meat, goose and guinea fowl - 1073 - Production - 5510 - tonnes") %>%
  filter(Entity== "World") %>% 
    group_by(Entity, Year)

pt_world_long <- pt_world %>% 
  pivot_longer(cols= "Sheep & Goat":"Goose & Guinea fowl",
               names_to= "Type",
               values_to = "Amount")

plt_type1<- ggplot(pt_world_long, aes(x= Year,
                                    y= Amount, 
                                    fill= Type))+ 
    geom_area(alpha=0.6 , size=.5, colour="white")+
    scale_fill_viridis(discrete = T) +
    theme_minimal()
plt_type1
```
.content-box[In first figure, we see that the **dominant livestock types are poultry**, cattle (which includes beef and buffalo meat), pig, and sheep & goat to a lesser extent at global level.
]

---
class: middle, center
```{r fig2, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Meat production by livestock type, 1961 to 2018"}
plt_type2<- ggplot(pt_world_long, aes(x= Year,
                                     y= Amount,
                                     group= Type,
                                     fill= Type))+
    geom_area() +
    scale_fill_viridis(discrete = TRUE)+
    theme_minimal() +
    facet_wrap(~ Type, scale="free_y")
plt_type2
```
.content-box[From second figure, we can see the production of all major meat types have been increasing. But **the share of global meat types have changed significantly**. 
  - In 1960s poultry meat accounted for small portion; by 2010s its share has tripled. 
  - Beef and buffalo meat as a share of total meat production has nearly halved. 
  - Pig meat’s share has remained more constant.
]

---
class: middle, center
```{r tidydata, echo = FALSE , message = FALSE, warning = FALSE}
pd_type <- MT %>%
  select(-Code) %>% 
  rename("Sheep & Goat"= "Livestock Primary - Sheep and Goat Meat - 1807 - Production - 5510 - tonnes",
         "Beef & Buffalo"= "Livestock Primary - Beef and Buffalo Meat - 1806 - Production - 5510 - tonnes",
         "Pig"= "Livestock Primary - Meat, pig - 1035 - Production - 5510 - tonnes",
         "Wild Game"= "Livestock Primary - Meat, game - 1163 - Production - 5510 - tonnes",
         "Duck"= "Livestock Primary - Meat, duck - 1069 - Production - 5510 - tonnes",
         "Poultry"= "Livestock Primary - Meat, Poultry - 1808 - Production - 5510 - tonnes",
         "Horse"= "Livestock Primary - Meat, horse - 1097 - Production - 5510 - tonnes",
         "Camel"= "Livestock Primary - Meat, camel - 1127 - Production - 5510 - tonnes",
         "Goose & Guinea fowl"= "Livestock Primary - Meat, goose and guinea fowl - 1073 - Production - 5510 - tonnes") %>%
    group_by(Entity, Year) %>%
    pivot_longer(cols= "Sheep & Goat":"Goose & Guinea fowl",
               names_to= "Type",
               values_to = "Amount")
```

```{r cattle, echo = FALSE , message = FALSE, warning = FALSE}
pd_cattle <- pd_type %>% 
    filter(Type == "Beef & Buffalo") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>% 
    arrange(-Total)

kable(head(pd_cattle, 20), caption = "Beef and buffalo (cattle) meat production, 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center")
```

---
class: middle, center
```{r cattle-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Cattle production, 1961 to 2018"}
top_cattle<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Brazil")) %>% 
  filter(Type== "Beef & Buffalo") %>% 
  group_by(Entity)

ggplot(top_cattle, aes(x= Year, y= Amount, color= Entity))+
      geom_line()+
    scale_fill_viridis(discrete = TRUE) +
    theme_minimal()
```

.content-box[In first table, we see the global production of cattle (beef and buffalo) meat. From country's perspective, **The United States is the world’s largest beef and buffalo meat producer**. Other major producers are Brazil and China.
]

---
class: middle, center
```{r poultry, echo = FALSE , message = FALSE, warning = FALSE}
pd_poultry <- pd_type %>% 
    filter(Type == "Poultry") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>% 
    arrange(-Total)

kable(head(pd_cattle, 20), caption = "Poultry meat production, 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center")
```

---
class: middle, center
```{r , echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "poultry production, 1961 to 2018"}
top_poultry<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Brazil",
                       "Europe")) %>% 
  filter(Type== "Poultry") %>% 
  group_by(Entity)

ggplot(top_poultry, aes(x= Year, y= Amount, color= Entity))+
  geom_line()+
  scale_fill_viridis(discrete = TRUE) +
  theme_minimal()
```

.content-box[In second table, we can see the production of poultry, like cattle production, **the United States is still the world’s largest producer.** China and Brazil are also large poultry producers. Collectively, Europe is also a major poultry producer, just below the United States.
]

---
class: middle, center
```{r pig, echo = FALSE , message = FALSE, warning = FALSE}
pd_pigmeat <- pd_type %>% 
    filter(Type == "Pig") %>% 
    group_by(Entity) %>% 
    summarise(Total= sum(Amount))%>% 
    arrange(-Total)

kable(head(pd_pigmeat, 20), caption = "Pig meat production, 1961-2018", booktabs = T)%>%
kable_material(c("striped", "hover"), position = "center")
```

---
class: middle, center
```{r , echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "pig production, 1961 to 2018"}
top_pigmeat<- pd_type %>% 
  filter(Entity %in% c("United States",
                       "China",
                       "Germany")) %>% 
  filter(Type== "Pig") %>% 
  group_by(Entity)

ggplot(top_pigmeat, aes(x= Year, y= Amount, color= Entity))+
  geom_line()+
  scale_fill_viridis(discrete = TRUE) +
  theme_minimal()
```

.content-box[But for pigmeat production , **China dominates global output, producing just short of half of total pigmeat.** The other major producers include the United States, Germany.
]